What We Eval in the Shadows

### 2021-04-16 paper/main.tex
Expression of eval: comparison with JS

\paragraph{Discussion} The variety of uses of \eval is evidenced by the number
of different forms observed in CRAN. In comparison, JavaScript \eval usage was more straightforward and more predictable as reported by \citet{oopsla12b}. Nevertheless, simple forms dominate, and there are many cases where \eval could be replaced by less powerful constructs.

>>>>

\paragraph{Discussion} The variety of uses of \eval is evidenced by the number
of different forms observed in CRAN. In comparison, JavaScript \eval usage was more straightforward and more predictable as reported by \citet{oopsla12b}, with 98.6\% of the sites with only one form. Nevertheless, simple forms dominate in R also, and there are many cases where \eval could be replaced by less powerful constructs.
